% !TeX program = lualatex

\documentclass[10pt,letterpaper,english]{moderncv} 
\moderncvstyle{banking} 

\definecolor{color0}{rgb}{0,0,0}% black
\definecolor{color1}{rgb}{0.749,0.341,0}% orange
\definecolor{color2}{rgb}{0., 0.37254902,  0.5254902}% dark grey

\usepackage[utf8]{inputenc}
\usepackage[margin=1in]{geometry}
\usepackage{babel}
\usepackage{tagging}
\usepackage{xparse}



% Tags:
%\usetag{details}
\usetag{physics}
\usetag{cern}


\firstname{Henry F.}
\familyname{Schreiner}
%\title{CV}
\address{1114 Camino La Costa Apt. 1020}{78752 Austin, TX}

\phone{512-660-9247} 
\email{henryschreineriii@utexas.edu}
\homepage{iscinumpy.blogspot.com}
\social[linkedin]{henryiii}
\social[github]{henryiii}
%\social[twitter]{henryschreiner3}


\NewDocumentCommand{\cvaward}{s m m m m m g}{%
\IfNoValueTF{#7}{%
\cventry{#2}{\textnormal{#6}}{#4: \textnormal{#3}}{#5}{}{}%
}{%
\IfBooleanTF{#1}{%
\cventry{#2}{\textnormal{#6: \emph{#7}}}{#4: \textnormal{#3}}{#5}{}{}%
}{%
\cventry{#2}{\textnormal{#6:}}{#4: \textnormal{#3}}{#5}{}{\emph{#7}}%
}%
}}

\begin{document}

\let\oldnullthing\null
\renewcommand{\null}{}
\makecvtitle
\renewcommand{\null}{\oldnullthing}
\vspace*{-10mm}
\section{Education}
\cventry{2010--2016}{Ph.D. in Experimental High Energy Physics}{University of Texas at Austin}{Austin, TX}{} % {GPA 3.8}
{\textcolor{red}{Defense: March 2016; Graduation: May 2016}} 

\cventry{2006--2009}{B.S. in Theoretical Physics}{Angelo State University}{San Angelo, TX}{GPA: 4.0} %
{December 2009, Summa Cum Laude, Distinguished Student for the College of Sciences}

\section{Doctoral Thesis}
\cvitem{Title}{Muon Tracking and Reconstruction}
\cvitem{Supervisor}{Roy Schwitters}
\cvitem{Description}{Used comparisons with GEANT4 simulations of targets and data from multiple experiments to
	show discrepancy in accepted low energy muon spectrum. Detailed a novel measurement of the low energy muon spectrum
	preformed in Lake Travis, Austin, TX. Explored new imaging techniques to search for new internal features inside a sealed Mayan pyramid in Belize. }

\section{Experience}
\subsection{Research}
\cventry{2010-2016}{MayaMuon Research Group}{University of Texas at Austin}{Austin, TX}{}{Installed detectors and a solar system in Belize, tomographic reconstruction and tracking.}
\tagged{details}{
\cvlistitem{Rebuilt and improved reconstruction code, 60-100x speedup, with C implementation of projection core with object oriented bindings for Matlab and Python systems and a GUI for on-site analysis in each.}
\cvlistitem{Built 3D reconstruction algorithm and voxel projections, including GPU versions.}
\cvlistitem{Built a GEANT4 simulation of the muon detectors, with multithreading and OpenMPI, on the TACC supercomputers.}
\cvlistitem{Prepared a new computer system and related components for the detectors, moved to ARM architecture, designed new parts and built them in the machine shop.}
\cvlistitem{Built a full featured threaded GUI in Python for on-site detector operation, compatible with all operating systems, including iOS.}
\cvlistitem{Automated the operation of the detectors for autonomous remote installations.}
\cvlistitem{During four trips to Belize, assisted in the construction of a remote autonomous solar power installation and serviced two detectors, including weeks of component troubleshooting.}
\cvlistitem{Rebuilt the data acquisition system from the ground up in C++11.}
\cvlistitem{Prepared a new public facing website for the project in less than 24 hours, built several private websites.}
}

\cventry{2008}{Physics REU}{Northwestern University}{Evanston, IL}{}{Theoretical condensed matter physics on DFT computer simulations of NiTi for predictions of new doped alloys.}

\cventry{2007--2010}
{Physics, Mathematics, Geology}
{Angelo State University}
{San Angelo, TX}
{}{Wavelet methods and their use in imaging and compression.\\
Mapped the Dagger Mountain Anticline in Big Bend, TX in ArcGIS.\\
A study of higher order gravitational effects of a non-spherical object on a probe.}


\subsection{Vocational}
\cventry{2010--2016}{Head Teaching Assistant, Teaching Assistant}{University of Texas at Austin}{Austin, TX}{}{}
\tagged{details}{
\cvlistitem{Managed 4-8 TAs responsible for up to 300 students, taught a lab section.}
\cvlistitem{Rewrote the lab manual with all new figures and several new labs, in \LaTeX.}
\cvlistitem{Rewrote all the Capstone and Excel lab files.}
\cvlistitem{Managed ordering replacement supplies for the lab.}
\cvlistitem{Implemented and taught an optional Excel workshop.}
\cvlistitem{Designed and machined new balanced mass hangers for harmonic motion lab.}
\cvlistitem{Automated many of the lab management tasks in Python, \LaTeX, and HTML.}
\cvlistitem{Rebuilt and managed the public facing website for the lab.}
\cvlistitem{Filmed prelab videos for all the labs, including computer animated concept sequences.}
}


\cventry{2010}{Special Projects Assistant}{Angelo State University}{San Angelo, TX}{}{}
%Content Management System and Course Management System upgrades, and tech support.

\subsection{Selected Projects}
\cventry{2015-}{Release manager, Color library author}{Plumbum: \textnormal{a Python package with 35,000 downloads per month}}{}{}{}
\cvitem{Blender 3D:}{Built Blender to GEANT4 GDML export add-on, molecule plotter, and 4D function plotter}
\cvitem{\LaTeX:}{Built a custom class used for multiple University of Texas Ph.D. theses}

\tagged{details}{
\cvitem{ASU SPS}{Participated in a cross-country SPS road trip to local middle and high schools to raise awareness about physics, wrote and managed a laser light show.}
\cvitem{Video}{Created a promotional video and animated footage for SPS.}
\cvitem{Websites}{Wrote a wiki for a retired faculty member, built a site for the Honor society, implemented a CMS as webmaster for SPS.}
\cvitem{Programming}{Contributed to several open-source projects, including infix, argcomplete and IPython.}
\cvitem{UT Law School}{Wrote a script for location-based data processing.}
}

\tagged{physics}{
	\section{Highlighted Graduate Classes}
	\cvitem{High Energy}{Quantum Field Theory I \&\ II, Physics of Sensors, Intro to particle physics}
	\cvitem{Other}{High Performance Scientific Computing with GPUs, Solid State Physics I, Statistical Methods, Methods of Mathematical Physics}
}

\section{Computer Skills}
\cvitem{Languages}{C++11, C++, C, Python, Cython, Matlab, \LaTeX, Bash, CUDA, HTML, Lua, PHP}
\cvitem{Toolsets}{GEANT4, Boost, HDF5, ROOT, OpenMP, MPI, PyQt, Pandas, Tikz}
\cvitem{Toolchains}{Git, CMake, Sphinx, Doxygen, Nikola}
\cvitem{Other}{2D, 2.5D, and 3D technical artist}
\tagged{details}{
\cvitem{Programs}{Blender, ArcGIS, LyX, Office, Gimp, Inkscape, Autodesk Inventor}
}



\tagged{details}{
\section{Interests}

\cvitem{Hobbies}{Computer modeling and animation, electronics projects, photography and amateur film-making, special effects and compositing, physics simulations, scientific illustrations in 3D, 2D, and 2.5D}
\cvitem{Projects}{Filmed and animated a short film: \emph{Brothers of the Force}}
}
\section{Results}
\subsection{Awards}

\cvaward{2015}
{Fall Meeting}
{American Geophysical Union}
{San Francisco, CA}
{Outstanding Student Paper Award}%
{Measurement Over Large Solid Angle of Low Energy Cosmic Ray Muon Flux}

\cvaward{2010}
{Academic Excellence Committee}
{Angelo State University}
{San Angelo, TX}
{2010 Distinguished Student Award for College of Sciences}

\cvaward{2009}
{Pi Mu Epsilon Mathfest}
{Society of Industrial and Applied Mathematics}
{Portland, OR}
{Outstanding Student Exposition and Research in Applied Mathematics}%
{Edge Effects in the Use of Wavelets for Partial Image Reconstruction}

\cvaward{2009}
{Alpha Chi National Convention}
{Alpha Chi}
{Indianapolis, IN}
{Certificate of Appreciation}

\cvaward{2009}
{Annual Meeting}
{Texas Academy of Sciences}
{Junction, TX}
{Amir Moez Award for Best Student Presentation in Mathematics, Abstract award}%
{Wavelet Matrix Completion Methods and Their Effects In Image Compression\\
\textnormal{Honorable Mention:}
The Controversial Origin of the Dagger Mountain Anticline, Big Bend National Park, Texas}


\cvaward{2009}
{Mathematics Problem of the Month}
{Angelo State University}
{San Angelo, TX}
{Winner}

\cvaward*{2008}
{Mathematical Contest in Modeling}
{COMAP}
{}
{Honorable Mention}%
{Sudoku Generator Model}

\cvaward{2008}
{REU}
{Northwestern University}
{Evanston, IL}
{Certificate of Achievement}

\cvaward{2008}
{APS -- Texas Section}
{University of Texas at El Paso}
{El Paso, TX}
{Student Presentation Award}


\subsection{Other Presentations}
\cvaward*{2013}
{High Energy Physics}
{University of Texas at Austin}
{Austin, TX}
{Lunch Seminar}%
{Computing Environments}

\cvaward*{2012}
{High Energy Physics}
{University of Texas at Austin}
{Austin, TX}
{Qualifier}%
{From Images to Quantitative Understanding of Muon Tomography}

\cvaward{2009}
{Slow Pitch Seminar}
{Angelo State University}
{San Angelo, TX}
{Three Mathematics ``slow pitch'' seminars over wavelets and cryptology}

\cvaward{2009}
{Alpha Chi Induction}
{Angelo State University}
{San Angelo, TX}
{Invited lecture for Alpha Chi induction ceremony}

\cvaward{2007}
{Joint Spring Meeting}
{Texas Sections of APS, AAPT, and SPS}
{Abilene, TX}
{\emph{Characterization of near earth objects via orbital perturbations: A numerical study}} %http://meetings.aps.org/link/BAPS.2007.TSS07.SPS2.1


\subsection{Co-Authored Presentations}

\cvaward{2008}
{Joint Meeting}
{Geological Society of America}
{Houston, TX}
{\emph{Dagger Mountain, Big Bend National Park, West Texas Does Not Overlie a Laccolith}}

\cvaward{2009}
{Joint Meeting}
{Geological Society of America}
{Portland, OR}
{\emph{Folding on the Flanks of the Southernmost Laramide Uplift, Big Bend Region, Texas}}

\subsection{Posters}



\cvaward{2015, 2013}
{UT Physics Open House}
{University of Texas at Austin}
{Austin, TX}
{High Energy Physics Poster, 2015 Group Leader}

\cvaward{2009}
{Student Research Showcase}
{Angelo State University}
{San Angelo, Texas}
{4 posters over 3 different fields}

\cvaward{2008}
{Quadrennial Congress}
{Sigma Pi Sigma}
{Fermilab, IL}
{Poster}

\subsection{Written Publications}
\cvitem{Future}{\textcolor{red}{Waiting on data}: Report on Belize Tomography (Science)}
\cvitem{June 2016}{\textcolor{red}{In preparation}: A Measurement of the Ultra Low Energy Muon Spectrum (Phys. Rev. Letters)}
\cvitem{May 2016}{\textcolor{red}{Waiting on review}: Muon Tomography and Detector Design (Nuclear Instr. and Methods)}
\cvitem{2013-2015}{University of Texas's PHY102M lab manual rewrite.}
\cvitem{2013}{Classified project report}
\cvitem{2010}{Assisted Angelo State University's modern lab manual rewrite.}


\section{Activities and Organizations}
\cvitem{2008--2009}{President of Pi Mu Epsilon, local chapter, at Angelo State University.}
\cvitem{2008-2009}{Webmaster, Society of Physics Students, local chapter, at Angelo State University.}
\cvitem{2009}{Executive Committee member, Society of Physics Students, local chapter, at Angelo State University.}

\subsection{Honor societies}
Sigma Pi Sigma \textbullet\ Pi Mu Epsilon \textbullet\ Alpha Chi \textbullet\ National Dean's List


\subsection{Scholarships and Grants}
\cvitem{2007-2009}{Carr Academic Scholarship}
\cvitem{2008-2009}{Carr Research Scholarship}
\cvitem{2007-2008}{H. R. Dawson Alumni Textbook Scholarship}
\cvitem{2007}{M. W. Everhart Scholarship}
\cvitem{2006}{RAO/Pollard Scholarship}

\section{References}
\begin{cvcolumns}

\cvcolumn{Dr. Roy F. Schwitters}{
University of Texas at Austin\\
Department of Physics\\
1 University Station C1600\\
Austin, TX 78712\\
(512) 471-9962\\
\emaillink{schwitters@physics.utexas.edu}}
%
\cvcolumn{Dr. Linda E. Reichl}{
The University of Texas at Austin\\
Department of Physics\\
1 University Station C1600\\
Austin, TX 78712\\
(512) 471-7253\\
\emaillink{reichl@mail.utexas.edu}
}

\cvcolumn{Dr. Martin L. Barlett}{
The University of Texas at Austin\\
ARL -- Signal Physics\\
PO Box 8029\\
Austin, TX 78713\\
(512) 835-3413\\
\emaillink{barlett@arlut.utexas.edu}}

\end{cvcolumns}


  
\tagged{cern}{
\begin{cvcolumns}
\cvcolumn{Dr. Peter Onyisi}{
The University of Texas at Austin\\
Department of Physics\\
1 University Station C1600\\
Austin, TX 78712\\
(512) 475-9129\\
\emaillink{ponyisi@utexas.edu}}
\end{cvcolumns}

}


%\clearpage
%-----       letter      -----
% recipient data
%\recipient{Company Recruitment team}{Company's name\\Street address\\Zip Code City}
%\date{Date}
%\opening{Dear Sir or Madam,}
%\closing{Yours faithfully,}
%\enclosure{enclosures}          % use an optional argument to use a string other than "Enclosure", or redefine \enclname
%\makelettertitle
%\makeletterclosing
\end{document}
